\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usetheme{Madrid}
\title{Tech-Skills Project Overview}
\author{COMP3420 Case Study}
\date{\today}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Motivation}
  \begin{itemize}
    \item Original idea: measure corporate \emph{hypocrisy}.
    \item Compare companies proclaiming technology-driven growth with their actual board composition.
    \item Many talked the talk but had few technologists on the board.
    \item Evolved into exploring trading strategies based on directors' backgrounds.
  \end{itemize}
\end{frame}

\begin{frame}{Data Sources}
  \begin{itemize}
    \item SEC EDGAR filings (e.g., DEF~14A, 10-K) provide information on directors and company statements.
    \item BoardEx datasets with detailed director profiles.
    \item Submissions index with ticker--CIK mappings.
    \item OpenAI models for NLP extraction of tables and text.
  \end{itemize}
\end{frame}

\begin{frame}{Pipeline Overview}
  \begin{enumerate}
    \item Download filings and BoardEx data, load into PostgreSQL.
    \item Extract textual and tabular information from filings.
    \item Use OpenAI APIs to parse director skills, compensation, and committee roles.
    \item Build a website summarising each company's board skills matrix.
  \end{enumerate}
\end{frame}

\begin{frame}{NLP Components}
  \begin{itemize}
    \item Sentence segmentation and pronoun resolution on proxy statements.
    \item Classification of director expertise using OpenAI.
    \item Optionally apply sklearn for additional analysis (clustering, similarity).
    \item Potential use of Keras models for custom sequence processing.
  \end{itemize}
\end{frame}

\begin{frame}{Measuring \enquote{Technologist} Presence}
  \begin{itemize}
    \item Each director assigned a technology score based on keywords and profile analysis.
    \item Scores aggregated to create an overall board tech score.
    \item Companies ranked by how strongly they emphasise technology versus board composition.
  \end{itemize}
\end{frame}

\begin{frame}{Trading Strategy Concept}
  \begin{itemize}
    \item Hypothesis: boards with genuine tech expertise deliver better long-term performance.
    \item Combine tech-score trends with market data to test strategies.
    \item Use Python for backtesting (pandas, sklearn). Future work may include neural nets via Keras.
  \end{itemize}
\end{frame}

\begin{frame}{Current Status}
  \begin{itemize}
    \item Database schemas for filings, directors, and compensation are set up with SQL scripts.
    \item Automated batch queries to OpenAI gather director details.
    \item Website generation summarises boards and tech evidence.
    \item Further analysis and trading models remain experimental.
  \end{itemize}
\end{frame}

\begin{frame}{How to Run}
  \begin{enumerate}
    \item Configure PostgreSQL connection in \texttt{db.conf}.
    \item Run SQL setup scripts (\texttt{schema.sql}, \texttt{etl.sql}).
    \item Use \texttt{extract\_tickers.py} and \texttt{fetch\_forms\_from\_edgar.py} to obtain filings.
    \item Process data with \texttt{extract\_director\_compensation.py} and \texttt{process\_director\_compensation.py}.
    \item Generate the website via \texttt{boards\_website\_generator.py}.
  \end{enumerate}
\end{frame}

\begin{frame}{Future Directions}
  \begin{itemize}
    \item Improved NLP models for role detection and sentiment analysis.
    \item Cross-reference market performance to validate hypotheses.
    \item Expand to global filings and other skill areas beyond technology.
  \end{itemize}
\end{frame}

\begin{frame}
  \centering
  \huge Questions?
\end{frame}

\end{document}
